Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-12 RR_manuscript/Draft_RR.Rmd
🐛 - fixes #161
♻️ - edit rr with uptodate results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(patchwork)
library(brms)
library(extraDistr)
library(faux)
library(tidybayes)
library(here)
library(googlesheets4)
```

@@

```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"), error = FALSE)
```
<!-- END:FIGURE -->

@@

```{r 'procedural', echo=FALSE, fig.cap="(ref:procedural)", out.width="100%"}
knitr::include_graphics(here::here("figs", "procedure_plot.png"), error = FALSE)
```
<!-- END: FIGURE -->

@@

```{r load-models, message=FALSE, warning=FALSE}
msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

@@

# number of analyses
no_analyses = nrow(msa_models)

@@

meta_intercept_prereg <- fixef(meta_bm_prereg)
meta_random_prereg <- ranef(meta_bm_prereg)

@@

meta_intercept <- fixef(meta_bm)
meta_random <- ranef(meta_bm)

@@

meta_intercept_nest <- fixef(meta_bm_nest)
meta_random_nest <- ranef(meta_bm_nest)

@@

According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95% credibility.
This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.

@@

Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95% credibility.
This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95% CrI for team in the second non-preregistered model is 0-0.05 standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(patchwork)
library(brms)
library(extraDistr)
library(faux)
library(tidybayes)
library(here)
library(googlesheets4)
library(broom.mixed)
```

@@

```{r forkingPaths, echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"), error = FALSE)
```
<!-- END:FIGURE -->

@@

```{r procedural, echo=FALSE, fig.cap="(ref:procedural)", out.width="100%"}
knitr::include_graphics(here::here("figs", "procedure_plot.png"), error = FALSE)
```
<!-- END: FIGURE -->

@@

```{r load-models, message=FALSE, warning=FALSE}
msa_mean_sd_df <- read_csv("data/analyses/msa_mean_sd_df.csv") %>%
  filter(transformation == "none", mean > 10)

msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

@@

# number of analyses
no_analyses <- msa_models %>%
  select(animal, model_n) %>%
  distinct() %>%
  nrow()

@@

meta_intercept_prereg <- fixef(meta_bm_prereg)
meta_random_prereg <- ranef(meta_bm_prereg)
meta_bm_prereg_tidy <- tidy(meta_bm_prereg)

@@

meta_intercept <- fixef(meta_bm)
meta_random <- ranef(meta_bm)
meta_bm_tidy <- tidy(meta_bm)

@@

meta_intercept_nest <- fixef(meta_bm_nest)
meta_random_nest <- ranef(meta_bm_nest)
meta_bm_nest_tidy <- tidy(meta_bm_nest)

@@

According to the meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.

@@

Based on the first non-preregistered model, the group-level standard deviation for model ID is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)` standard units, at 95% credibility.
This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95% CrI for team in the second non-preregistered model is `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

### 2022-09-12 RR_manuscript/Draft_RR.tex
♻️ - edit rr with uptodate results

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0-0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

>>>>

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
